---
title: "Rugby-try-analysis"
author: "Josh Drummond"
date: "11/04/2020"
output:
  prettydoc::html_pretty:
    theme: leonids
    highlight: github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview 

This activity provides you with the opportunity to practice and work through a reproducible data analysis project. In this activity we will be exploring rugby try scoring data.

## Load required packages

```{r packages, message=FALSE}
library(tidyverse) # include all required packages at the start
```

## Data source

The data set used in this activity has been saved in the 2017_super-rugby_try-source-data.csv file.

## Read data

Read in the `batting.csv` file using the `read_csv()` function from the `readr` package. 

```{r read_data, message=FALSE} 
# read in the data
# data dir should be in the working dir
df <- read_csv("2017_super-rugby_try-source-data.csv")
```

## Checking the data

Check the structure of the data file using `str()`:

```{r structure}
str(df)
```

Check the first 6 rows of the data file using `head()`

```{r head}
head(df)
```

Check the last 6 rows of the data file using `tail()`

```{r tail}
tail(df)
```

### Graph Analysis

This graph shows the attacking team and how often across the season they were recorded as the attacking team. 

``` {r attacking}

ggplot(data = df) +
  geom_bar(mapping = aes(x = attacking_team), stat = "count")

```
